The Influence of Connectivity on Dung Beetle Communities

### 2025-07-23 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
beetle weights

All dung beetles were counted and identified to species using @nemes_illustrated_2015 and @edmonds_taxonomic_2023. Fifteen individuals of each species with adequate captures were dried to equilibrium and weighed for biomass measurements. **[EDIT SENTENCE ABOVE AS FOLLOWS:** Fifteen individuals of each species with adequate captures (was there a numeric cutoff?) were dried at XXX degrees until they reached a stable mass. We weighed each beetle using a BRAND, MODEL microbalance, except for species whose individuals were extremely small. Individual biomass for these species was estimated by weighing batches of N = 5  (i.e., ---------) or N = 3  (i.e., ---------) beetles and then calculating the average biomass per beetle. These values of individual biomass were then used to estimate the total dung beetle biomass -- all species combined and for each individual species - in each block and patch. **]** Voucher specimens for each species will be deposited at the Florida State Collection of Arthropods upon completion of all analyses.

>>>>

All dung beetles were counted and identified to species using @nemes_illustrated_2015 and @edmonds_taxonomic_2023. Fifteen individuals of each species with adequate captures were dried and weighed for biomass measurements. Ten species had the required counts for weighing which I dried in drying oven until all specimen reached a stable mass. I weighed each beetle using an Ohaus Adventurer Pro AV53 microbalance, with the exception of individuals whose weights were extremely small. Individual biomass for these species was estimated by weighing in batches of N = 3 (i.e., *Ateuchus lecontei*), N = 5 (i.e., *Onthophagus pennsylvanicus*), or N = 15 (i.e., *Aphodius alloblackburneus*) and then calculated by average biomass per beetle. Values for individual biomass were then used to estimate the totall dung beetle biomass for each -- all species combined and for each individual species - in each block and patch. Voucher specimens for each species will be deposited at the Florida State Collection of Arthropods upon completion of all analyses.
